---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# examples

<!-- badges: start -->
<!-- badges: end -->

This package provides some functions to support the "Hacking RStudio" workshop given during useR! 2019.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ColinFay/user2019workshop", subdir = "examples")
```

## Part 1

[addins.dcf](inst/rstudio/addins.dcf)

+ [Takes a selected word, and look for it on Wikipedia.](R/wik.R)

+ [Inserts a random cat picture in a](R/cat_picture.R).

## Part 2

Snippets are at [inst/snippets.txt](inst/snippets.txt) 

+ Create a FALSE snippet that inserts TRUE and vice-versa Create a ggplot skeleton snippet

+  a snippet that inserts a list of library()

+ Create a snippet that add a random {cowsay} to your script 

Theme is at [inst/colin.rstheme](inst/colin.rstheme), based on "Subway_ Paris (dark).tmTheme" from https://tmtheme-editor.herokuapp.com/#!/editor/theme/Paris%20(dark)

Things added starts at line 768

```{r eval = FALSE}
rstudioapi::addTheme("inst/colin_theme.rstheme", apply = TRUE, force = TRUE)
```

This theme:

+ Add a background image to RStudio

+ Change some colors from RStudio

## Part 3

RMarkdown template for twitter scrapping [inst/rmarkdown/templates/rtweet/](inst/rmarkdown/templates/rtweet/)